The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-03-23 paper.tex
finished all basic ross corrections

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
\usepackage{subcaption}
\usepackage{lscape}
\usepackage[LGRgreek]{mathastext}

@@

% Abstract of the paper
\begin{abstract}
We present dynamical measurements for 77 star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high-redshift Universe.
We have made careful comparisons to other samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
The mean dispersion value of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\sim3$ in other samples.
However only $34 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
These random motions are likely to provide significant pressure support against gravity on the galactic disk scale.
\end{abstract}

@@

Recent cosmological volume simulations provide subgrid recipes for the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope ({\em {\em HST}}) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.

@@

There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016a,Harrison2017,Straatman2017,Ubler2017}.
Systematic differences in measurement and modelling techniques at high-redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
Additionally, there has been increasing focus in the last few years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high-redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk result in a decrease in the observed rotational velocities \citep{Burkert2010}. 
Different interpretations of the gaseous velocity dispersions and their role in providing pressure support against gravity also complicate the evolutionary picture. \\

In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focussing on the spatially resolved properties of main sequence SFGs at $z\sim3.5$, a time when the universe was building to peak activity.
There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts.
For example: \textbf{(1)} How do the physical conditions of the ISM such as electron density and ionisation parameter change as a function of spatial position within the galaxy, and what does this tell us about the application of strong line metallicity calibrators at high-redshift?
\textbf{(2)} What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
\textbf{(3)} What are the dynamical properties of main sequence galaxies at this early stage in their lifetimes? 
\textbf{(4)} What is the connection between the gas phase metallicity and  kinematics, particularly in terms of inflows and outflows of material?

This paper focusses on the third question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
By making use of KMOS we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed in IFS at $z > 3$. \\

The structure of the paper is as follows. In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction, leading to stacked datacubes for each of the KDS galaxies.
In \cref{sec:analysis} we describe the derivation of morphological and kinematic properties for our galaxies, explaining the kinematic modelling approach and the beam-smearing corrections which lead to intrinsic measurements of the rotation velocities, $V_{C}$, and velocity dispersions $\sigma_{int}$ for each of the galaxies classified as morphologically isolated and spatially resolved in the [O~{\sc III}]$\lambda$5007 emission line.
\cref{sec:results} presents an analysis of these derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible physical mechanisms driving these.
We present our conclusions in \cref{sec:conclusion}.
Throughout this work we assume a standard $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).

\section{SURVEY DESCRIPTION, SAMPLE SELECTION AND OBSERVATIONS}\label{sec:Survey_and_data}
\subsection{The KDS survey description and sample selection}\label{subsec:survey_intro}
The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\sim3.5$, probing a representative section of the galaxy main sequence.
The addition of this data approximately triples the number of galaxies observed in IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution. 
The two key science goals of the KDS are to investigate the resolved kinematic properties of high-redshift galaxies in the epoch of galaxy formation, particularly the fraction of rotating disks, the degree of disk turbulence and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
To achieve this we require very deep exposure times in excess of 7 hours on source to reach the S/N required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten and to achieve adequate S/N across several ionised emission lines within individual spatial pixels (spaxels).
Consequently, this is some of the deepest spectroscopic data available for this redshift.

\subsubsection{Sample selection}\label{subsubsec:sample_selection}
Target selection for the KDS sample is designed to pick out SFGs at $z \sim 3.5$, supported by deep multi-wavelength ancillary data.
Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the K-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the H-band, both of which are observable with KMOS.
From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest S/N and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities. 
To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well studied fields that have a previous spectroscopic detection (see details below).
Predominantly, the galaxies have been selected for spectroscopic follow up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
However, a subset of the selected cluster galaxies in the SSA22 field were blindly detected in Ly$\alpha$ emission during a narrowband imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z \sim 3.09$ \citep{Steidel2000}.
We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main sequence at this redshift.

@@

\begin{table*}
\centering
\begin{threeparttable}
\caption{Summary of KDS pointing statistics for the full observed sample of 77 galaxies}
\label{tab:pointings}
\begin{tabular}{c c c c c c c c c c c c c c}

 \hline
Pointing & Environment & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band$^{a}$ & Exp (ks) & PSF ($^{\prime\prime}$)$^{b}$  \\
 \hline
 GOODS-S-P1 & FIELD & 03:32:22 & -27:52:51 & 20 & 16 & 80 & 13 & 65 & 2 & 17 & K & 32.4 & 0.50 \\
GOODS-S-P2 & FIELD & 03:32:35 & -27:43:15 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & K & 31.8 & 0.52 \\
SSA22-P1 & CLUSTER & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & HK & 27.8 & 0.57 \\
SSA22-P2 & FIELD & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
 \hline
\end{tabular}
\begin{tablenotes}
      \small
      \item $^{a}$ We also observed the two GOODS-S pointings in the H-band to cover the [O~{\sc II}]$\lambda$3727,3729 emission lines and a description of these observations will be given in a future work.
      \item $^{b}$ The PSF values correspond to measurements in the K-band.
      \item $^{*}$ Note that the Merger percentage is computed with respect to the number of resolved galaxies; the other percentages are computed with respect to the total number of galaxies observed in that pointing.
    \end{tablenotes}
  \end{threeparttable}
  \end{table*}

Two of the FIELD environment pointings (GOODS-S-P1;GOODS-S-P2; see Table \ref{tab:pointings}) are selected within GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
We select targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully exclude those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the K-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we select two regions where $\sim 20$ targets can be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
In GOODS-S-P1 and GOODS-S-P2 we observe 20 and 17 galaxies respectively.\footnote{We note that the number of observed galaxies in GOODS-S-P2 does not include two targets which were later found to have $z < 0.5$.}

\subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
A single CLUSTER environment pointing (SSA22-P1; see Table \ref{tab:pointings}) is selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
Hundreds of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS \citep{Shapley2003,Nestor2013}.
A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011,Yamada2012a} and archival {\em HST ACS} and {\it WFC3} provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so for the CLUSTER environment pointing we fill the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).

We also add a further FIELD environment pointing to the south of the main SSA22 spatial overdensity where the density of galaxies is typical (SSA22-P2).
In SSA22-P1 and SSA22-P2 we observe 19 and 21 galaxies respectively.
In summary we have chosen three FIELD environment pointings and a single CLUSTER environment pointing across GOODS-S and SSA22, comprising a total of 77 galaxies, as described in Table \ref{tab:pointings}. \footnote{Additional pointings in the COSMOS and UDS fields were originally scheduled as part of the GTO project, however 50$\%$ of the observing time was lost to bad weather during these visitor mode observations.}

@@

\begin{figure*}
    \centering \hspace{-1.3cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{rest_colour.png}
    \end{subfigure} \hspace{+0.4cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{main_sequence.png}
    \end{subfigure}
    \caption{{\it Left:} The distribution of 49 KDS galaxies (see \cref{subsubsec:sed_fitting}) in rest-frame UVJ colour space is plotted, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
    Also plotted in this plane are $\sim4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey, with the filled squares denoting the density in of galaxies in that region.
    We use the galaxy selection criteria defined in \protect\cite{Whitaker2012a} to highlight star-forming and quiescent regions (motivated by the age sequence of quiescent galaxies), finding that the KDS galaxies are all clearly in the star-forming region and overlap with the highest density of 3D-{\em HST} targets.
    {\it Right:} We plot the location of the same 49 KDS galaxies in the SFR versus M$_{\star}$ plane, using the same symbol convention. 
    The same GOODS-S galaxies from the 3D-{\em HST} survey \protect\citep{Brammer2012,Momcheva2016} at $3.0 < z < 3.8$ are plotted with the filled squares as a reference for the typical relationship between SFR and $M_{\star}$.
    The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
    We include the MS relation evaluated at $z=3.5$ (the median redshift of the KDS sample) described in \protect\cite{Speagle2014} and given in equation \protect\ref{eq:speagle_ms} throughout the text as the green line, with the discrepancy between the two relations representating the expected main sequence evolution between these redshifts. 
    Within the typical uncertainties (see error bars) the KDS sample is representative of $z\sim3.5$ SFGs.}
    \label{fig:main_sequence}
\end{figure*}

>>>>

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
\usepackage{subcaption}
\usepackage{lscape}
\usepackage[LGRgreek]{mathastext}
\usepackage{enumitem}

@@

% Abstract of the paper
\begin{abstract}
We present dynamical measurements for 77 star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high-redshift Universe.
We have made careful comparisons to other samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
The mean dispersion value of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\sim3$ in other samples.
However only $34 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
These random motions are likely to provide significant pressure support against gravity on the galactic disk scale.
\end{abstract}

@@

Recent cosmological volume simulations provide subgrid recipes for the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collapse, mergers and outflows e.g. \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulations to reproduce.
Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
When interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope ({\em HST}), these data provide information about the range of physical processes which are driving galaxy evolution.
In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to be assembled rapidly \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.

@@

There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016a,Harrison2017,Straatman2017,Ubler2017}.
Systematic differences in measurement and modelling techniques at high-redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
Additionally, there has been increasing focus in the last few years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high-redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk could result in a decrease in the observed rotational velocities \citep{Burkert2010}. 
Different interpretations of the gaseous velocity dispersions and their role in providing pressure support against gravity also complicate the evolutionary picture. \\

In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focusing on the spatially resolved properties of main sequence SFGs at $z\sim3.5$, a time when the universe was building to peak activity.
There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts: \begin{enumerate}[label=(\roman*)] \item How applicable are strong line metallicity calibrators at high redshift? \item  What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
\item What are the dynamical properties of main sequence galaxies at this early stage in their lifetimes? 
\item What is the connection between the gas phase metallicity and  kinematics, particularly in terms of inflows and outflows of material? \end{enumerate}

This paper focuses on the third question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
By making use of KMOS (with integration times of 7.5-9 hours) we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed in IFS at $z > 3$. \\

The structure of the paper is as follows. In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction, leading to stacked datacubes for each of the KDS galaxies.
In \cref{sec:analysis} we describe the derivation of morphological and kinematic properties for our galaxies, explaining the kinematic modelling approach and the beam-smearing corrections which lead to intrinsic measurements of the rotation velocities, $V_{C}$, and velocity dispersions $\sigma_{int}$ for each of the galaxies classified as morphologically isolated and spatially resolved in the [O~{\sc III}]$\lambda$5007 emission line.
\cref{sec:results} presents an analysis of these derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible underlying physical mechanisms.
We present our conclusions in \cref{sec:conclusion}.
Throughout this work we assume a standard $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).

\section{SURVEY DESCRIPTION, SAMPLE SELECTION AND OBSERVATIONS}\label{sec:Survey_and_data}
\subsection{The KDS survey description and sample selection}\label{subsec:survey_intro}
The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\sim3.5$, probing a representative section of the galaxy main sequence.
The addition of this data approximately triples the number of galaxies observed in IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution. 
The two key science goals of the KDS are to investigate the resolved kinematic properties of high-redshift galaxies in the peak epoch of galaxy formation, particularly the fraction of rotating disks, the degree of disk turbulence and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and a `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
To achieve this we require very deep exposure times in excess of 7 hours on source to reach the S/N required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten and to achieve adequate S/N across several ionised emission lines within individual spatial pixels (spaxels).
Consequently, the KDS is one of the deepest spectroscopic datasets available at this redshift.

\subsubsection{Sample selection}\label{subsubsec:sample_selection}
Target selection for the KDS sample is designed to pick out SFGs at $z \sim 3.5$, supported by deep multi-wavelength ancillary data.
Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the {\it K}-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the {\it H}-band, both of which are observable with KMOS.
From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest S/N and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities. 
To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well studied fields that have a previous spectroscopic detection (see details below).
Predominantly, the galaxies were originally selected for spectroscopic follow up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
However, a subset of the selected cluster galaxies in the SSA22 field were blindly detected in Ly$\alpha$ emission during a narrowband imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z \sim 3.09$ \citep{Steidel2000}.
We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main sequence at this redshift.

@@

\begin{table*}
\centering
\begin{threeparttable}
\caption{This table summarises the KDS pointing statistics for the full observed sample of 77 galaxies.
The columns list the pointing name, the galaxy environment probed, the central pointing coordinates, the number of observed, detected, resolved and merging objects as described in \protect\cref{subsubsec:datareduction}, the waveband observed with KMOS, the exposure time and the PSF measured in the {\it K}-band.}
\label{tab:pointings}
\begin{tabular}{c c c c c c c c c c c c c c}

 \hline
Pointing & Environment & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band$^{a}$ & Exp (ks) & PSF ($^{\prime\prime}$)$^{b}$  \\
 \hline
 GOODS-S-P1 & FIELD & 03:32:22 & $-$27:52:51 & 20 & 16 & 80 & 13 & 65 & 2 & 17 & K & 32.4 & 0.50 \\
GOODS-S-P2 & FIELD & 03:32:35 & $-$27:43:15 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & K & 31.8 & 0.52 \\
SSA22-P1 & CLUSTER & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
SSA22-P2 & FIELD & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & HK & 27.8 & 0.57 \\

 \hline
\end{tabular}
\begin{tablenotes}
      \small
      \item $^{a}$ We also observed the two GOODS-S pointings in the {\it H}-band to cover the [O~{\sc II}]$\lambda$3727,3729 emission lines and a description of these observations will be given in a future work.
      \item $^{b}$ The PSF values correspond to measurements in the {\it K}-band.
      \item $^{*}$ Note that the Merger percentage is computed with respect to the number of resolved galaxies; the other percentages are computed with respect to the total number of galaxies observed in that pointing.
    \end{tablenotes}
  \end{threeparttable}
  \end{table*}

Two of the FIELD environment pointings are selected within the GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with $ 0.06^{\prime\prime}$ pixel scale and $ \sim 0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
We selected targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully excluded those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the {\it K}-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we selected two regions where $\sim 20$ targets could be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
In GOODS-S-P1 and GOODS-S-P2 we observe 20 and 17 galaxies respectively (see Table \ref{tab:pointings}).\footnote{We note that the number of observed galaxies in GOODS-S-P2 does not include two targets which were later found to have $z < 0.5$.}

\subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
A single CLUSTER environment pointing was selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
Hundreds of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS \citep{Shapley2003,Nestor2013}.
A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011,Yamada2012a} and archival {\em HST ACS} and {\it WFC3} provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the {\it K}-band which is free from OH features and so for the CLUSTER environment pointing we filled the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).

We also added a further FIELD environment pointing to the south of the main SSA22 spatial overdensity where the density of galaxies is typical (SSA22-P2).
In SSA22-P1 and SSA22-P2 we observe 19 and 21 galaxies respectively.
In summary we have chosen three FIELD environment pointings and a single CLUSTER environment pointing across GOODS-S and SSA22, comprising a total of 77 galaxies, as described in Table \ref{tab:pointings}. \footnote{Additional pointings in the COSMOS and UDS fields were originally scheduled as part of the GTO project, however 50$\%$ of the observing time was lost to bad weather during these visitor mode observations.}

@@

Our data for the 77 KDS targets were observed using KMOS, which is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the {\it K}-band grating has a spectral resolution of $R \sim 4200$ ({\it H}-band $R \sim 4000$).
\subsubsection{Observations}\label{subsubsec:Obs}
